Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
edit demos and implementation

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can install browser extensions and run
  arbitrary Javascript in the developer console to change them. However,
  this malleability is only accessible to programmers with knowledge of
  HTML and Javascript. To broaden access to customization, our prior
  work developed an approach that empowers end-users to customize
  websites without traditional programming via a browser extension
  called Wildcard. However, Wildcard only opened part of the
  customization process to end-users, and still required programmers to
  write site-specific adapters to map website data to a table view
  through which the customizations are made. This means that end-users
  can only customize a website if a programmer has written an adapter
  for it. Furthermore, end-users do not have the ability to extend
  adapters in order to perform new customizations or repair adapters to
  fix broken customizations.

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization} which enables end-users to create,
  extend and repair adapters by demonstration. We describe three design
  principles that guided our system's development and are applicable to
  other end-user web scraping and customization systems: (a) users
  should be able to scrape data and use it in a single, unified
  environment, (b) users should be able to extend and repair the
  programs that scrape data via demonstration and (c) users should
  receive live feedback during their demonstrations.

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{end-user programming, software customization, web browser extensions}

@@

Wildcard has a key limitation. In order to enable end-users to customize
a website, a Javascript programmer first needs to code an adapter that
specifies how to scrape the website content and set up a bidirectional
synchronization with Wildcard's table view. Even though programmers can
share adapters with end-users, this means that an end-user can only use
Wildcard on websites where some programmer has already written an
adapter. Additionally, if an adapter doesn't scrape the desired data, or
stops functioning correctly when a website changes, an end-user has no
recourse to extend or repair it on their own.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Unified Environment}: Users should be able to scrape data and
  interact with the scraped data in a single, unified environment. This
  minimizes the barrier to fluidly switching back and forth between the
  two tasks, rather than treating them as entirely independent tasks.
\item
  \textbf{Editing By Demonstration}: Users should be able to not only
  create programs for scraping data by demonstration, but also extend
  and repair the programs by demonstration. This enables users to build
  on other user's work, and is especially important in the context of
  web scraping since programs that scrape data sometimes break as the
  underlying website changes.
\item
  \textbf{Live Programming}: Users should receive live feedback as they
  perform demonstrations. The system should indicate how it is
  generalizing from the user's example and what the resulting data will
  look like, so that the user can adjust their demonstrations on the fly
  and quickly arrive at the desired result.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row
  (Part 3).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (Part 3 and 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}

@@

Jen uses Wildcard on timeanddate.com. In addition to sorting the list of
holidays in a year by the day of the week, she also wants to sort them
by category so she can view all the federal holidays together.
Previously, she would have needed to find a programmer to help her edit
the adapter code to incorporate this additional data, but using our
system's support for \textbf{editing by demonstration}, Jen can extend
the adapter herself.

@@

One important difference is that our algorithm only accepts row elements
that have direct siblings with a similar structure. We refer to this as
the \emph{row-sibling} constraint. Later in this section, we describe
how the constraint provides a useful simplification of the wrapper
induction task and discuss the resulting limitations this puts on our
system in a section that follows.

@@

The user performs a demonstration by clicking on element (a) in
Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
traverses upwards from the demonstrated element, considering each
successive parent element ((b1), (c1) and (d) in
Figure~\ref{fig:algorithm}) as a potential candidate for the row
element. For each parent element \(n\), the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a column selector \(s\) that when executed on \(n\) only
  returns the demonstrated element
\item
  for each sibling \(m\) of \(n\), execute \(s\) on \(m\) and record
  whether the selector returned an element. Intuitively, if the selector
  returns an element, this suggests that the sibling \(m\) has some
  parallel structure to \(n\)
\item
  compute \(n_{siblings}\), the number of sibling elements of \(n\) for
  which \(s\) returned an element
\end{enumerate}

Notice how the \emph{row-sibling} constraint simplifies the problem: row
candidates without siblings that return an element after \(s\) is
executed on them ((b1) in Figure~\ref{fig:algorithm}) have
\(n_{siblings}\) = 0, thus disqualifying them. Furthermore, a candidate
element \(n\) is only accepted as the row element if the row selector
\(n_{selector}\) associated with it only matches itself and elements
that are its direct siblings.

The algorithm stops traversing upwards once it reaches the BODY element.
Then, it generates a selector \(n_{selector}\) for each \(n\) and
discards any \(n\) with an \(n_{selector}\) that matches elements that
are either not itself or a direct sibling. Finally, the algorithm picks
an \(n\) with the largest, positive \(n_{siblings}\), preferring nodes
lower in the tree as a tiebreaker. \(n_{selector}\) is used as the
selector for the row and \(s\) is used as the selector for the column.
The row and column selectors are used to generate a scraping adapter
which returns the DOM elements corresponding to a superhero data row in
the table and sets up the bidirectional synchronization.

@@

The row-sibling constraint we mentioned earlier is important for the end
goal of customization because row elements that are not direct siblings
may not represent data on the website that should be related as part of
the same table by customizations such as sorting and filtering.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/limitations.png}
  \caption{\label{fig:limitations} Our generalization algorithm cannot generalize on websites with the shown layouts. The elements with the blue border correspond to rows of the data in each layout respectively.}
\end{figure*}

For \emph{Generalization Limitation 1} shown in
Figure~\ref{fig:limitations}, without the constraint that row elements
have to be direct siblings, the row generalization algorithm could
determine the row selector to be \emph{.avenger} (elements with blue
border) because it matches the largest number of parallel structures
(has the largest \(n_{siblings}\)). While this may be the correct result
for the task of extraction, it is not for the task of customization. The
selector matches all rows across the two tables (elements with green
border) so the sorting and filtering customizations could place rows in
the incorrect table and thereby distort what the tables represent.
Because of this, our system currently does not support such layouts but
we plan to explore the possibility of extracting multiple tables from a
website and joining them.

For \emph{Generalization Limitation 2} shown in
Figure~\ref{fig:limitations}, website contains one table of data in
which rows are made up of the alternating H1 and SPAN tags (elements
with blue border). For the task of extraction, the DOM elements can be
scraped using the shown classes to output a table in which the values of
the H1 tags form the first column and the values of the SPAN tag form
the second column. For the task of customization, our system would need
to know what the row boundaries were in order for customizations such as
sorting and filtering to work as expected. In Wildcard, this can be done
with a hand-coded adapter by creating artificial row boundaries. In
\emph{Generalization Limitation 2}'s layout, an artificial row boundary
could be created by representing a row as an H1 tag and the SPAN tag
that immediately follows it. These artificial rows would form a single
unit which would not distort the website after a sorting or filtering
customization. We plan to explore how such artificial row boundaries
might be created via demonstration in order to support these structures
(which are not uncommon, and can be seen, for example, in HackerNews).

Another major limitation of our system is our current lack of support
for scraping data loaded after the initial websites render as the user
scrolls. Hand-coded adapters can specify event listeners on the DOM to
re-execute the scraping code when new data is loaded as a user scrolls.
In future work, will we provide a mechanism for end-users to specify
when the adapter created via demonstration should re-execute its
scraping code in response to user scrolling. There is a similar
limitation for websites that have paged data but it is not clear how
suitable such pages are for customization to begin with.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Websites are malleable: users can run code in the browser to customize
  them. However, this malleability is typically only accessible to
  programmers with knowledge of HTML and Javascript. Previously, we
  developed a tool called Wildcard which empowers end-users to customize
  websites through a data table interface without doing traditional
  programming. However, there is a limit on end-user flexibility with
  Wildcard, because programmers need to create site-specific adapters
  mapping website data to a table view. This means that end-users can
  only customize a website if a programmer has written an adapter for
  it, and cannot extend or repair existing adapters.

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization}. It enables end-users to create,
  extend and repair adapters, by performing concrete demonstrations of
  how the webpage UI maps to a data table. We describe three design
  principles that guided our system's development and are applicable to
  other end-user web scraping and customization systems: (a) users
  should be able to scrape data and use it in a single, unified
  environment, (b) users should be able to extend and repair the
  programs that scrape data via demonstration and (c) users should
  receive live feedback during their demonstrations.

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{end-user programming, software customization, web scraping, programming by example}

@@

Wildcard has a key limitation. In order to enable end-users to customize
a website, a programmer first needs to code a Javascript adapter that
specifies how to scrape the website content and set up a bidirectional
synchronization with Wildcard's table view. Even though programmers can
share adapters with end-users, this means that an end-user can only use
Wildcard on websites where some programmer has already written an
adapter. Additionally, if an adapter doesn't scrape the desired data, or
stops functioning correctly when a website changes, an end-user has no
recourse to extend or repair it on their own.

@@

\begin{itemize}
\tightlist
\item
  \textbf{Unified Environment}: Users should be able to scrape data and
  interact with the scraped data in a single, unified environment. This
  minimizes the barrier to fluidly switching back and forth between the
  two tasks, rather than treating them as entirely independent tasks.
\item
  \textbf{Editing By Demonstration}: Users should be able to not only
  create programs for scraping data by demonstration, but also extend
  and repair the programs by demonstration. This enables users to build
  on other users' work, and is especially important in the context of
  web scraping since scrapers break as the underlying website changes.
\item
  \textbf{Live Programming}: Users should receive live feedback as they
  perform demonstrations. The system should indicate how it is
  generalizing from the user's example and what the resulting data will
  look like, so that the user can adjust their demonstrations on the fly
  and quickly arrive at the desired result.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The selected row of data is annotated in the page with a border, to
  indicate that she will be demonstrating values from within that row
  (Part 3).
\item
  The selected column of data is highlighted in the page with a green
  background, to show how the system has generalized her demonstration
  across all the rows in the data (Part 4).
\item
  A table view appears at the bottom of the screen, and displays how the
  values will appear in the data table (Part 5).
\end{itemize}

@@

Jen has previously used Wildcard to customize timeanddate.com, sorting
holidays by day of the week. She comes up with a new customization idea:
sorting holidays by category so she can view all the federal holidays
together. The current site adapter she is using does not populate the
category column in the table, so she needs to extend the adapter. She
can immediately perform the extension in the context of the page, using
our system's support for \textbf{editing by demonstration}.

@@

One important difference is that our algorithm only accepts row elements
that have direct siblings with a similar structure. We refer to this as
the \emph{row-sibling} constraint. Later, we describe how the constraint
provides a useful simplification of the wrapper induction task and
discuss the resulting limitations this puts on our system.

@@

The user performs a demonstration by clicking on element (a) in
Figure~\ref{fig:algorithm} containing ``Tony Stark.'' Our algorithm
traverses upwards from the demonstrated element, considering each
successive parent element ((b1), (c1) and (d) in
Figure~\ref{fig:algorithm}) as a potential candidate for the row
element. For each parent element \texttt{el}, the process is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  compute a column selector \texttt{selector} that, when executed on
  \texttt{el}, only returns the demonstrated element
\item
  for each sibling \texttt{el\textquotesingle{}} of \texttt{el}, execute
  \texttt{selector} on \texttt{el\textquotesingle{}} and record whether
  the selector returns an element. If it does, this suggests that
  \texttt{el\textquotesingle{}} has some parallel structure to
  \texttt{el}.
\item
  compute \(n_{siblings}\), the number of sibling elements of
  \texttt{el} which have parallel structure.
\end{enumerate}

Notice how the \emph{row-sibling} constraint simplifies the problem. Row
candidates without siblings with parallel structure ((b1) in
Figure~\ref{fig:algorithm}) have \(n_{siblings}\) = 0, thus
disqualifying them.

The algorithm stops traversing upwards once it reaches the BODY element.
It chooses the element with the largest positive value of
\(n_{siblings}\) as the row element, preferring nodes lower in the tree
as a tiebreaker. It then generates a \emph{row selector} which returns
the row element and all its direct siblings. The column selector is the
selector that traverses from the row element to the demonstrated data
value. These row and column selectors are then used to generate a
scraping adapter which returns the DOM elements corresponding to a data
row in the table and sets up the bidirectional synchronization.

@@

The row-sibling constraint we mentioned earlier is important for the end
goal of customization because row elements that are not direct siblings
may not represent data on the website that should be related as part of
the same table by customizations such as sorting and filtering. In
Figure~\ref{fig:limitations} we demonstrate two examples where this
limitation becomes relevant.

\begin{figure*}
  \includegraphics[width=\textwidth]{media/limitations.png}
  \caption{\label{fig:limitations} Two example pages where our generalization algorithm does not currently work. The elements with the blue border correspond to rows of the data in each layout respectively.}
\end{figure*}

\emph{Generalization Limitation 1} shows a case where the data is
displayed in a grouped structure. Without the constraint that row
elements have to be direct siblings, the row generalization algorithm
could determine the row selector to be \emph{.avenger} (elements with
blue border) because it matches the largest number of parallel
structures (has the largest \(n_{siblings}\)). While this may be the
correct result for the task of extraction, it is not necessarily
suitable for the task of customization. When the user sorts and filters,
this could result in rows moving between the two tables, disrupting the
nested layout and producing a confusing result. Because of this, our
system currently does not support such layouts. In the future, we may
explore the possibility of extracting multiple tables from a website and
joining them together.

\emph{Generalization Limitation 2}, also in
Figure~\ref{fig:limitations}, shows a case where the website contains
one table of data in which rows are made up of alternating H1 and SPAN
tags (elements with blue border). This poses a challenge because each
row does not correspond directly to a single DOM element; instead, each
row consists of multiple consecutive DOM elements without any grouped
structure. Moving the rows when customizing the webpage would require
treating multiple consecutive elements as a single row. This is
supported in the underlying Wildcard system, but not yet by our tool.

Our system also does not support scraping data loaded after the initial
websites render as the user scrolls. Site adapters hand-coded in
Javascript can specify event listeners on the DOM to re-execute the
scraping code when new data is loaded as a user scrolls. In future work,
we plan to provide a mechanism for end-users to specify when a
demonstrated adapter should re-execute its scraping code in response to
user scrolling. We also do not support scraping data across multiple
pages of related data, but this context poses more fundamental
challenges to the idea of web customization, since users would somehow
need to perform customizations across multiple pages in coordination.
